---
title: "p8105_hw5_yz4436"
author: "Yuanhao Zhang"
date: "2022-11-16"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


## Problem 1

The code chunk below imports the data in individual spreadsheets contained in `./data/zip_data/`. To do this, I create a dataframe that includes the list of all files in that directory and the complete path to each file. As a next step, I `map` over paths and import data using the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r}
full_df = 
  tibble(
    files = list.files("data/zip_data/"),
    path = str_c("data/zip_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn't tidy -- data are wide rather than long, and some important variables are included as parts of others. The code chunk below tides the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 

## Problem 2

Import the raw dataset.
```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv")
```

The raw data is about homicides in 50 large U.S. cities, and there are `r nrow(homicide_df)` rows and `r ncol(homicide_df)`, which are `r colnames(homicide_df)`

```{r}
homicide_df =
  homicide_df %>%
  janitor::clean_names() %>%
  mutate(
    city_state = str_c(city, ",", state)
  )
```

Summarize within cities to obtain the total number of homicides and the number of unsolved homicides.
```{r}
number_df = 
  homicide_df %>%
  mutate(
    total = 1,
    without_arrest = ifelse(disposition == "Closed without arrest", 1, 0),
    Open_No = ifelse(disposition == "Open/No arrest", 1, 0)
  ) %>%
  group_by(city_state) %>%
  summarize(
    total_homicide = sum(total),
    unsolved_homicide = sum(without_arrest) + sum(Open_No)
  )

```

For the city of Baltimore, MD, I create a function called prop_tests with prop.test to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object.

```{r}
baltimore = 
  number_df %>%
  filter(city_state == "Baltimore,MD")


prop_tests = function(city) {
  prop.test(city$unsolved_homicide, city$total_homicide, conf.level = 0.95) %>%
    broom::tidy()
}
prop_tests(baltimore) %>%
  select(estimate, conf.low, conf.high)

```

* For the city of Baltimore, MD, after applying the broom::tidy to this object, we could find that the proportion of homicides that are unsolved is about `r prop_tests(baltimore)$estimate`, and the 95% confidence intervals is (`r prop_tests(baltimore)$conf.low`, `r prop_tests(baltimore)$conf.high`).


Now run prop.test for each of the cities in the dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. I use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.
```{r}
all_cities = 
  number_df %>%
  mutate(
    each_city = purrr::map2(.x = unsolved_homicide, .y = total_homicide, ~prop.test(x = .x, n = .y, conf.level = 0.95)),
    tidy_cities = purrr::map(.x = each_city, ~broom::tidy(.x))
  ) %>%
  unnest(tidy_cities) %>%
  select(city_state, estimate, conf.low, conf.high)
```

I create a plot that shows the estimates and CIs for each city.

```{r}
all_cities %>% 
  ggplot(aes(fct_reorder(city_state, estimate), estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(
    title = "Estimates and 95% CIs of estimates for each city of 50 large U.S. cities",
    x = "City, State", y = "Estimates"
  )
```

# Problem 3
First set the following design elements:n=30, σ=5 for x∼Normal[μ,σ].
```{r}
sim_mean_sd = function(n = 30, mu = 0, sigma = 5) {
  
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  ) 
  t.test (sim_data, mu = 0, alpha = 0.05, conf.level = 0.95) %>% 
    broom::tidy()
}
```

Set μ=0. Generate 5000 datasets with α=0.05.
And then repeat for μ={1,2,3,4,5,6}. Set mu start from 0 to 6 in order to draw plots later. 
```{r}
zero_results_df = 
  expand_grid(
    mu = 0,
    iter = 1:5000
  ) %>% 
  mutate(
    estimate_df = map(.x = mu, ~sim_mean_sd(mu = .x))
  ) %>% 
  unnest(estimate_df) %>%
  select(mu, iter, estimate, p.value)

sim_results_df = 
  expand_grid(
    mu = 0:6,
    iter = 1:5000
  ) %>% 
  mutate(
    estimate_df = map(.x = mu, ~sim_mean_sd(mu = .x))
  ) %>% 
  unnest(estimate_df) %>%
  select(mu, iter, estimate, p.value)
```


Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. 

```{r}
sim_results_df %>%
  mutate(
    rejected = ifelse(p.value < 0.05, 1, 0)
  ) %>%
  group_by(mu) %>%
  summarize(
    prop = sum(rejected) / 5000
  ) %>%
  ggplot(aes(x = mu, y = prop)) + 
  geom_point() +
  geom_line() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(
    title = "Proportion of times the null was rejected for different mu",
    x = "mu",
    y = "Rejected proportion"
  )
```

Describe the association between effect size and power.
* According to the plot, we could see that as the true mu increases, proportion of times the null was rejected also increases. From the trend of the plot, we could also find that the rejected proportion increased very fast in the beginning part, then change slower and approach to 1 finally. We could say the larger effect size, the larger power.

