---
title: "p8105_hw5_yz4436"
author: "Yuanhao Zhang"
date: "2022-11-16"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


## Problem 1

The code chunk below imports the data in individual spreadsheets contained in `./data/zip_data/`. To do this, I create a dataframe that includes the list of all files in that directory and the complete path to each file. As a next step, I `map` over paths and import data using the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r}
full_df = 
  tibble(
    files = list.files("data/zip_data/"),
    path = str_c("data/zip_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn't tidy -- data are wide rather than long, and some important variables are included as parts of others. The code chunk below tides the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 

## Problem 2

Import the raw dataset.
```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv")
```

The raw data is about homicides in 50 large U.S. cities, and there are `r nrow(homicide_df)` rows and `r ncol(homicide_df)`, which are `r colnames(homicide_df)`

```{r}
homicide_df =
  homicide_df %>%
  janitor::clean_names() %>%
  mutate(
    city_state = str_c(city, ",", state)
  )
```

Summarize within cities to obtain the total number of homicides and the number of unsolved homicides.
```{r}
number_df = 
  homicide_df %>%
  mutate(
    total = 1,
    without_arrest = ifelse(disposition == "Closed without arrest", 1, 0),
    Open_No = ifelse(disposition == "Open/No arrest", 1, 0)
  ) %>%
  group_by(city_state) %>%
  summarize(
    total_homicide = sum(total),
    unsolved_homicide = sum(without_arrest) + sum(Open_No)
  )

```

For the city of Baltimore, MD, I create a function called prop_tests with prop.test to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object.

```{r}
baltimore = 
  number_df %>%
  filter(city_state == "Baltimore,MD")


prop_tests = function(city) {
  prop.test(city$unsolved_homicide, city$total_homicide, conf.level = 0.95) %>%
    broom::tidy()
}
prop_tests(baltimore) %>%
  select(estimate, conf.low, conf.high)

```

* For the city of Baltimore, MD, after applying the broom::tidy to this object, we could find that the proportion of homicides that are unsolved is about `r prop_tests(baltimore)$estimate`, and the 95% confidence intervals is (`r prop_tests(baltimore)$conf.low`, `r prop_tests(baltimore)$conf.high`).
